Why Donors Donate?

### 2020-09-14 analysis/05_market_simulator.Rmd
Fixed issue with Org 1 and duplicate selectInput for Persona 1. Market Share values still not exactly matching with excel version.

beta$levels = c("Amnesty International",
                "Greenpeace", 
                "Oxfam", 
                "Red Cross",
                # Org Issue
                "Environment", 
                "Human rights",
                "Refugee relief",
                # Transparency
                "Engages in transparency",
                # Financial Accountability
                "Engages in financial accountability",
                # Funding
                "Handful of wealthy private donors", 
                "Government grants",
                # Gov Relations
                "Criticized by government",
                "Under government crackdown")

# Org Reactive Element
df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    # beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$org1_id] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$ai_value[beta$levels %in% input$org2_id] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    # beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ai_value[beta$levels %in% input$org3_id] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    # beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$ai_value[beta$levels %in% input$org4_id] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

                        "Yes", 

@@

                        "Complete trust",

@@

                        "At least once a month",

@@

                        "Complete trust",

@@

                        "At least once a month", 

@@

                        "Yes",

@@

                        "At least once a month",

@@

                        "Involved",

@@

                        "Involved",

@@

@@

@@

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

@@

    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1

@@

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

@@

# Orgnization
org1 <- org_data[,2]

@@

  # Organization name inputs
  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  # Type of value
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # Persona name inputs
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

@@

  ggplotly(df %>% 
             # Only care about the Market Share right now
             filter(Type == "Market Share") %>% 
             # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c( "#FFC30B", "#28a153", "#c23838")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})

@@

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes"))

@@

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust"))

@@

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

@@

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month'))

@@

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved'))

@@

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member'))

@@

textInput("ai_id",
          label = "Organization Name",
          value = "Organization 1",
          placeholder = "Enter Organiation Name")

selectInput("org1_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))

@@

selectInput("org2_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("gp_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))

@@

selectInput("org3_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("ox_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))

@@

selectInput("org4_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Green Peace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("rc_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))

>>>>

beta$levels = c("Amnesty International",
                "Greenpeace", 
                "Oxfam", 
                "Red Cross",
                # Org Issue
                "Environment", 
                "Human rights",
                "Refugee relief",
                # Financial Transparency
                "Engages in transparency",
                # Financial Accountability
                "Engages in accountability",
                # Funding
                "Handful of wealthy private donors", 
                "Government grants",
                # Gov Relations
                "Criticized by government",
                "Under government crackdown")

# Org Reactive Element
df <- reactive({

  #Amnesty International
    beta$ai_value <- 0
    # beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$org1_id] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1

  #Greenpeace
    beta$gp_value <- 0
    # beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$org2_id] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1

  #Oxfam
    beta$ox_value <- 0
    # beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$org3_id] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1

  #Redcross
    beta$rc_value <- 0
    # beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$org4_id] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

                        "Yes (1)", 

@@

                        "Complete trust (1)",

@@

                        "At least once a month (1)",

@@

                        "Complete trust (2)",

@@

                        "At least once a month (2)", 

@@

                        "Yes (2)",

@@

                        "At least once a month (3)",

@@

                        "Involved (1)",

@@

                        "Involved (2)",

@@

                        "Active member (1)",

@@

                        "Active member (2)",

@@

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

@@

    beta_persona$p2_value[beta_persona$levels %in% input$p2_national_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_international_news] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_news_medium] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_follow_gov] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_travel_developing] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_pref] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_institution_trust] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_others_charitable] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_worship_attendence] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion_importance] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_religion] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_charity_importance] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_trust_in_charity] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_donation_amount] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_12] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_volunteer_frequency] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_personal_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_family_activism] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_religious_member] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_sport_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_art_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_labor_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_political_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_environmental_member] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_professional_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_humanitarian_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_consumer_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_other_member] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_gender] <- 1

    beta_persona$p2_value[beta_persona$levels %in% input$p2_marital_status] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_education] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_income] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_race] <- 1
    beta_persona$p2_value[beta_persona$levels %in% input$p2_age] <- 1

@@

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1

    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

@@

# Organization
org1 <- org_data[,2]

@@

  # Organization name inputs
  df[,2] <- rep(c(input$ai_id, input$gp_id, input$ox_id, input$rc_id),6)
  # Type of value
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # Persona name inputs
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

@@

  ggplotly(df %>% 
             # Only care about the Market Share right now
             filter(Type == "Market Share") %>% 
             # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})

@@

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c('No', "Yes (1)"))

@@

selectInput("p1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all",
                     "Very little trust",
                     "Little trust",
                     "Nuetral",
                     "Some trust",
                     "A lot of trust",
                     "Complete trust (1)"))

@@

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month (1)"))

@@

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust (2)"))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'At least once a month (2)'))

@@

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes (2)"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month (3)"))

selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not involved',
                     'Involved (1)'))

selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not involved',
                     'Involved (2)'))

@@

selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member (1)'))

@@

selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive member',
                     'Active member (2)'))

@@

textInput("ai_id",
          label = "Organization Name",
          value = "Organization 1",
          placeholder = "Enter Organization Name")

selectInput("org1_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

@@

selectInput("org2_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("gp_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

@@

selectInput("org3_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("ox_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))

@@

selectInput("org4_id",
            label = "Select Organization:",
            choice = c("Amnesty International",
                       "Greenpeace",
                       "Oxfam",
                       "Red Cross"))

@@

selectInput("rc_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in accountability",
                        "Engages in accountability"))
